---
	title: "02c-perfect-information-performance-metrics"
author: "Jessica Walsh"
date created: "12 Jan 2018"
output: pdf_document
---
	
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, cache=FALSE, autodep = TRUE,
											message = FALSE, warning = FALSE, fig.height = 6, fig.width = 10)
```
Here we test the performance of different HCRs with perfect information. 
These results show the output from: 
	
* 5 havest control rules, 
* across 5 different species, 
* for two different harvest control rules (bioeconomic coupling and one-way trip) and 
* two lengths of management period (5 and 20 yrs)
* 3 HCR bufffers

Current n = 600 for each scenario

We select the buffer of HCR that ensures 10% BBmsy >0.25 and maximises catch (relative to MSY) across all species and harvest dynamics. If the best buffers differ, we choose the most precautionary one.

###Management objectives
1.	Maintain median biomass at Bmsy 
2.  Maintain 10% percentile biomass > 25%BBmsy
3. 	Avoid collapsed fisheries (i.e. proportion of stocks B <25% Bmsy across full management period)
3.	Maintain sustainable harvest rate (F/Fmsy) 
4.  Avoid overfishing (i.e. median F > Fmsy)
5.	Maximise yield (catch) during management period (total catch over management period relative to fishing at Fmsy)

## Performance metrics

### MSE- Box plots
* B/Bmsy at end of management period of 5 years and 20 years (averaged over last 3 years)
* F/Fmsy at the end of management period of 5 and 20 years (averaged over last 3 years)
* Propotion of years dipping below 0.25 BBmsy.
* Change in B/Bmsy at end of management period since beginning of management (for those above and below Bmsy) at 5 and 20 years
* Change in F/Fmsy at end of management period since start of management (for those below and above Fmsy) at 5 and 20 years
* Total or mean catch over management years (relative to virgin biomass, MSY or yield if fished at Fmsy)
* St Dev of catches over management years (annual variation)

\newpage

```{r load_packages}
library(ggplot2)
library(knitr)
library(FLCore)
library(dplyr)
library(gridExtra)


sp_lookup = data.frame(c('BC','SA','PS','SJ','BF','CR'),
											 c('Rockfish','Sardine','Sole',
											 	'Tuna','Small Tuna',
											 	'Corvina'))
colnames(sp_lookup)<-c('Symbol', 'Name')

species <- factor(levels = c("BC","PS","SJ","SA","CR"))

sce_lookup = data.frame(c("ED03","ED03","OW","OW"),
												c("5", "20", "5","20"),
												c("ED03_05yr", "ED03_20yr","OW_05yr", "OW_20yr"))
colnames(sce_lookup) <- c("ED", "REA_YR", "scenario")

scenario <- factor(c("ED03_05yr", "ED03_20yr","OW_05yr", "OW_20yr"))
```

```{r set_parameters}
it = 1
#iters = 1
ts = 20					#TS	#length of catch time series before first assessment
#proj_yr = 20 		# num years to project forward
length_sim = 60 # num years in simulations

SP <- c("BC","PS","CR","SA","SJ")
ED <- c("ED03","OW")
REA_YR = c("5", "20")		# time after first assessment until second assessment
reps <- 1:600
#TS <- c(20, 60)
HCR <- c("HR4010","TAC4010","HRsw","TACsw","BAU")
BUF <- c(0.5, 0.6, 0.7, 0.75, 0.8, 0.9, 1.0)
```

```{r make_metric_dataframe_perfect_info, eval = FALSE}
# ##Create datafile that with all performance metrics across scenarios for perfect info
#last created 29/01/2018
#note: takes 5 hours 

## need to redo the data compiling if MSE rerun
if(!file.exists(file="../data-generated/performance_metrics_true_dat.rds")) {

require(doParallel)
registerDoParallel(cores = 3)
getDoParWorkers()

plyr::l_ply(SP, .paropts = list(.export=c("ED", "REA_YR", "reps","HCR", "BUF",
																					"it", "ts", "length_sim"),
																.packages = c("FLCore", "dplyr", "gridExtra")),
						.fun = function(sp) {
							
metrics_true <- data.frame(matrix(vector(), 0, 17, dimnames=list(c(), c("sp", "ts", "ed","j","rea_yr","buffer", "ctrl","BBmsy_final", "prop_10bmsy","change_bbmsy","FFmsy_final", "prop_abovefmsy","change_ffmsy", "catch_mean", "rel_catch_tot", "catch_relFmsy_mean", "catch_sd"))), stringsAsFactors=F)

							for (ed in ED) {
							#	for (sp in SP) {
									load(paste0("data-raw/sims-", sp,"-",ed,".Rdata"))
									true_refpts <- sims[[sp]]$brp@refpts
									Bmsy_sim <- true_refpts["msy", "biomass"] %>% an()
									Fmsy_sim <- true_refpts["msy", "harvest"] %>% an()
									Msy_sim <- true_refpts["msy", "yield"] %>% an()
							
								for (buffer in BUF) {
										buff_name <- buffer * 100
								
										for (j in reps) {
											filename_buf <- paste0(sp,"_TS",ts,"_",ed,"_rep",j,"_buf",buff_name)
											mse_runs_true <- readRDS(file=paste0("data-generated/mse_results/true/buffer",buff_name,"/",ed,"/mse_projection_",filename_buf,"_true.rds"))
									
											## Collect each performance metric for all scenarios
											for (rea_yr in REA_YR) {
												
												mgmt_yrs = (length_sim+1):(length_sim+an(rea_yr))
												years = (length_sim-(ts-1)):(length_sim+an(rea_yr))
												
											for (ctrl in HCR) {
													
													stock_proj <- eval(parse(text = paste0("mse_runs_true$stock_proj_", ctrl)))
													stock_proj <- FLCore::iter(stock_proj,it) %>%
														FLCore::trim(year=years)
													
													## B/Bmsy status at end of management period (mean of last 3 years)
													bbmsy <- FLCore::FLQuant(stock(stock_proj)/Bmsy_sim) %>%
														FLCore::as.data.frame() %>%
														dplyr::select(year, data)
													
													BBmsy_final <- mean(bbmsy$data[(length(bbmsy$data)-2):length(bbmsy$data)],na.rm=TRUE)
													
													## Prop of years that have a projected B/Bmsy below 25%Bmsy
													prop_25bmsy <- sum(bbmsy$data[bbmsy$year==mgmt_yrs] < 0.25) / an(rea_yr) * 100
													
													## Prop of years that have a projected B/Bmsy below 10%Bmsy
													prop_10bmsy <- sum(bbmsy$data[bbmsy$year==mgmt_yrs] < 0.10) / an(rea_yr) * 100
													
													##Change in B/Bmsy since start of management
													change_bbmsy <- bbmsy$data[bbmsy$year == max(years)] - bbmsy$data[bbmsy$year == (min(mgmt_yrs)-1)]  
													## F/Fmsy status at end of management period (mean of last 3 years)
													ffmsy <- FLQuant(fbar(stock_proj)/Fmsy_sim) %>%
														FLCore::as.data.frame() %>%
														dplyr::select(year, data)
													
													FFmsy_final <- mean(ffmsy$data[(length(ffmsy$data)-2):length(ffmsy$data)],na.rm=TRUE)
													
													## F/Fmsy status (proportion of years where F/Fmsy is above Fmsy)
													prop_abovefmsy <- sum(ffmsy$data[ffmsy$year==mgmt_yrs] > 1)/ an(rea_yr) * 100
													
													##Change in F/Fmsy since start of management 
													# (or should this be mean last 3 years - mean last 3 years before mgmt?)
													change_ffmsy <- ffmsy$data[ffmsy$year == max(years)]- ffmsy$data[ffmsy$year == (min(mgmt_yrs)-1)] 
													
													## Mean catch (across multiple iterations) per year in management period, relative to MSY
													catch_msy <- FLQuant(catch(stock_proj)/Msy_sim) %>%
														FLCore::as.data.frame() %>%
														dplyr::select(year, data)
													catch_mean <- mean(catch_msy$data[catch_msy$year==mgmt_yrs], na.rm=TRUE)
													
													## Mean catch per year in management period, relative to fishing at Fmsy
													#finding yield across management period if project forward with Fmsy
													catch_Fmsy <- catch(mse_runs_true$stock_proj_Fmsy) %>% 
														FLCore::trim(year=years) 
													
													catch_relFmsy <- FLQuant(catch(stock_proj)/catch_Fmsy) %>%
														FLCore::as.data.frame() %>%
														dplyr::select(year, data)
													catch_relFmsy_mean <- mean(catch_relFmsy$data[catch_relFmsy$year==mgmt_yrs], na.rm=TRUE)
													
													## Total catch across all years in management period (per repitition)
													rel_catch_vB <- FLQuant(catch(stock_proj)/as.numeric(sims[[sp]]$lh["v"])) %>%
														FLCore::as.data.frame() %>%
														dplyr::select(year, data)
													rel_catch_tot <- sum(rel_catch_vB$data[rel_catch_vB$year == mgmt_yrs], na.rm=TRUE)
													
													## Annual variation in catches (standard deviation for each repition) over management period relative to msy
													catch_sd <- sd(catch_msy$data[catch_msy$year==mgmt_yrs],	na.rm =TRUE)
													
													out <- data.frame(sp, ts, ed, buffer, j, rea_yr, ctrl, BBmsy_final, prop_25bmsy, prop_10bmsy, change_bbmsy,FFmsy_final, prop_abovefmsy, change_ffmsy, catch_mean, catch_relFmsy_mean, rel_catch_tot, catch_sd)

												metrics_true <- bind_rows(metrics_true,out)
													rm(out)
												}
											}
											message(filename_buf)
										}
									}
								}
						#	}
							saveRDS(metrics_true, file=paste0("data-generated/performance_metrics_true_dat_",sp,".rds"))
						}, .parallel = TRUE)

metrics_true_BC <- readRDS(paste0("data-generated/performance_metrics_true_dat_BC.rds"))
metrics_true_CR <- readRDS(paste0("data-generated/performance_metrics_true_dat_CR.rds"))
metrics_true_SA <- readRDS(paste0("data-generated/performance_metrics_true_dat_SA.rds"))
metrics_true_SJ <- readRDS(paste0("data-generated/performance_metrics_true_dat_SJ.rds"))
metrics_true_PS <- readRDS(paste0("data-generated/performance_metrics_true_dat_PS.rds"))

metrics_true_full <- bind_rows(metrics_true_BC,metrics_true_CR) %>%
	bind_rows(metrics_true_SA) %>% bind_rows(metrics_true_SJ) %>%
	bind_rows(metrics_true_PS)
saveRDS(metrics_true_full, paste0("data-generated/performance_metrics_true_dat.rds"))
metrics_true <- metrics_true_full
} else {
metrics_true <- readRDS(paste0("../data-generated/performance_metrics_true_dat.rds"))
}
 
```


```{r performance_metrics_true_plots_setup}
##Create plots for each metric
metrics_true <- readRDS(paste0("data-generated/performance_metrics_true_dat.rds"))

metrics_true$ctrl <- factor(metrics_true$ctrl,levels=(c("HR4010", "HRsw", "TAC4010",  "TACsw","BAU")))
metrics_true <- mutate(metrics_true, scenario = paste0(ed,"_",rea_yr,"yr"))
metrics_true$scenario <- factor(metrics_true$scenario, levels =c("ED03_5yr","ED03_20yr","OW_5yr","OW_20yr"))
metrics_true$sp <- factor(metrics_true$sp, levels = c("BC","CR","PS","SA","SJ"),labels = c("Rockfish","Corvina","Sole","Sardine","Tuna"))

plot_performance_metrics_true_together <- function(dat) {
	ggplot(dat, aes(as.factor(ctrl), perf_metric)) + 
		geom_boxplot(aes(fill=factor(ctrl))) +
		scale_fill_brewer(palette="Paired") +
		#scale_fill_manual (values=cols) +
		xlab("Harvest Control Rule") +
		facet_grid(scenario~sp) +
		theme_bw() +
		theme(axis.text=element_text(size=10),
					axis.title=element_text(size=14),
					#axis.title.y=element_text(margin=margin(10,10,0,0)),
					#axis.title.x=element_text(margin=margin(10,8,0,0)),
					axis.text.x=element_text(angle=90, vjust=0.4,hjust=1),
					plot.title=element_text(size=18),
					legend.title = element_blank())
}

#pdf(file = paste0("../plots/performance_metrics_true_plots.pdf"), width = 16, height = 9)

###BBmsy current ###
metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,buffer,ctrl,scenario,BBmsy_final) %>%
	rename(perf_metric = BBmsy_final)
pdf(file = paste0("plots/performance_metrics_true_plots_current_BBmsy_together.pdf"), width = 16, height = 9)
for (i in 1:length(BUF)) {
dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
plotx <- plot_performance_metrics_true_together(dat_temp) +
	geom_hline(yintercept = 1, linetype = "dashed") +
	ggtitle(paste("Current B/Bmsy status TRUE Info ",BUF[i])) +
	ylab("B/Bmsy (mean of last 3 yrs)") + 
	ylim(c(0,4))
print(plotx)
}
dev.off()

###Change in BBmsy###
# metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,buffer,ctrl,scenario,change_bbmsy) %>%
# 	rename(perf_metric = change_bbmsy)
# #pdf(file = paste0("plots/performance_metrics_true_plots_current_BBmsy_together.pdf"), width = 16, height = 9)
# for (i in 1:length(BUF)) {
# dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
# plotx <- plot_performance_metrics_true_together(dat_temp) +
# 	#ggtitle(paste("Change in B/Bmsy ", ed_plot, rea_year, "yrs")) +
# 	ggtitle("Change in B/Bmsy since first assessment") +
# 	ylab("Change in B/Bmsy") +
# 	geom_hline(yintercept = 0, linetype = "dashed") # +
# #	ylim(c(-2,2))
# print(plotx)
# }
# #dev.off()

### Prop of years that stocks were overfished (<25%Bmsy)
metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,buffer,ctrl,scenario,prop_25bmsy) %>%
	rename(perf_metric = prop_25bmsy)
for (i in 1:length(BUF)) {
dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
plotx <- plot_performance_metrics_true_together(dat = dat_temp) +
	ggtitle(paste("Prop. years overfished (<25%Bmsy)",BUF[i])) +
	ylab("Prop. years below 25% Bmsy")
print(plotx)
}

### Prop of years that stocks were collapsed (<10%Bmsy)
metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,buffer,ctrl,scenario,prop_10bmsy) %>%
	rename(perf_metric = prop_10bmsy)
for (i in 1:length(BUF)) {
dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
plotx <- plot_performance_metrics_true_together(dat= dat_temp) +
	ggtitle(paste("Prop. years with collapsed stock",BUF[i])) +
	ylab("Prop. years below 10% Bmsy")
print(plotx)
}

### FFmsy at end of management period
metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,buffer,ctrl,scenario,FFmsy_final) %>%
	rename(perf_metric = FFmsy_final)
pdf(file = paste0("plots/performance_metrics_true_plots_current_FFmsy_together.pdf"), width = 16, height = 9)
for (i in 1:length(BUF)) {
dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
plotx <- plot_performance_metrics_true_together(dat= dat_temp) +
	geom_hline(yintercept = 1, linetype = "dashed") +
	ggtitle(paste("F/Fmsy status - end of management period",BUF[i])) +
	ylab("F/Fmsy (mean of last 3 yrs)") +
	ylim(c(0,4))
print(plotx)
}
dev.off()

###Change in FFmsy###
metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,buffer,ctrl,scenario,change_ffmsy) %>%
	rename(perf_metric = change_ffmsy)
for (i in 1:length(BUF)) {
dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
plotx <- plot_performance_metrics_true_together(dat=dat_temp) +
	#ggtitle("Change in F/Fmsy since management") +
	ylab("Change in F/Fmsy") +
	geom_hline(yintercept = 0, linetype = "dashed")
print(plotx)
}

### Prop of years that stocks with overfishing (>Fmsy)
metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,ctrl,scenario,prop_abovefmsy) %>%
	rename(perf_metric = prop_abovefmsy)
for (i in 1:length(BUF)) {
dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
plotx <- plot_performance_metrics_true_together(dat=dat_temp) +
	ggtitle("Prop. years overfishing during management") +
	ylab("Prop. years above F/Fmsy")
print(plotx)
}

###Total catch over management period relative to virgin biomass ###
metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,buffer,ctrl,scenario,rel_catch_tot) %>%
	rename(perf_metric = rel_catch_tot)
for (i in 1:length(BUF)) {
dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
plotx <- plot_performance_metrics_true_together(dat=dat_temp) +
	#ggtitle(paste("Total catch, relative to virgin biomass", ed_plot, rea_year, "yrs")) +
	ggtitle("Total catch, relative to virgin biomass") +
	geom_hline(yintercept = 1, linetype = "dashed") +
	ylab("Total catch during management") #+
#	ylim(c(0,2))
print(plotx)
}

###mean annual catch during management period###
metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,buffer,ctrl,scenario,catch_mean) %>%
	rename(perf_metric = catch_mean)
#pdf(file = paste0("plots/performance_metrics_true_plots_catch_mean_together.pdf"), width = 16, height = 9)
for (i in 1:length(BUF)) {
dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
plotx <- plot_performance_metrics_true_together(dat= dat_temp) +
	ggtitle(paste("Mean catch/year, relative to MSY",BUF[i])) +
	geom_hline(yintercept = 1, linetype = "dashed") +
	ylab("Mean catch/year during management") #+
#	ylim(c(0,3))
print(plotx)
}
#dev.off()

###mean annual catch during management period, relative to yield at Fmsy###
metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,buffer,ctrl,scenario,catch_relFmsy_mean) %>%
	rename(perf_metric = catch_relFmsy_mean)
pdf(file = paste0("plots/performance_metrics_true_plots_catch_mean_together_Fmsy.pdf"), width = 16, height = 9)
for (i in 1:length(BUF)) {
dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
plotx <- plot_performance_metrics_true_together(dat= dat_temp) +
	ggtitle(paste("Mean catch/year, relative to FMSY", BUF[i])) +
	geom_hline(yintercept = 1, linetype = "dashed") +
	ylab("Mean catch/year during management, relative to yield at Fmsy") +
 ylim(c(0,3))
print(plotx)
}
dev.off()


###St dev of catches over management period ####
metrics_true_plot <- select(metrics_true,sp,ts,ed,j,rea_yr,buffer,ctrl,scenario,catch_sd) %>%
	rename(perf_metric = catch_sd)
#pdf(file = paste0("plots/performance_metrics_true_plots_catch_sd_together.pdf"), width = 16, height = 9)
#png(file = paste0("plots/performance_metrics_true_plots_catch_sd_together.png"), width = 10, height = 6, units = "in",res=600)
for (i in 1:length(BUF)) {
dat_temp <- subset(metrics_true_plot, buffer == BUF[i])
plotx <- plot_performance_metrics_true_together(dat=dat_temp) +
	ggtitle(paste("Annual variation in catches during mamagement",BUF[i])) +
	ylab("St dev of catches during management") #+
#	ylim(c(0,2))
print(plotx)
}
#dev.off()

```

\newpage

##Summary tables

* Proportion of stocks that go below 25% Bmsy (averaged across all management period) (overfished levels)
* Proportion of stocks that end the management period at F>Fmsy (overfishing)

```{r summary_tables, eval=TRUE}
metrics_true <- readRDS("data-generated/performance_metrics_true_dat.rds")

dat <- group_by(metrics_true, sp, ed, rea_yr, buffer, ctrl) %>%
	summarise(#prop_stocks_overfished = sum(BBmsy_final<0.25)/length(BBmsy_final),
		prop_stocks_not_overfished = sum(BBmsy_final>0.25)/length(BBmsy_final),
		av_bbmsy = median(BBmsy_final),
		pc10_bbmsy = quantile(BBmsy_final,0.1),
		av_ffmsy = median(FFmsy_final),
		prop_stocks_overfishing = sum(FFmsy_final>1) /length(FFmsy_final),
		prop_stocks_no_overfishing = sum(FFmsy_final<1) /length(FFmsy_final),
		mean_catch_low = sum(catch_mean<0.8)/length(catch_mean),
		av_catch_msy = median(catch_mean),
		av_catch_Fmsy = median(catch_relFmsy_mean),
		av_catch_variation =median(catch_sd))

buffer_dat_05 <- filter(dat, rea_yr == "5") %>%
	group_by(buffer, ctrl) %>%
	summarise(mean_bbmsy = mean(av_bbmsy),
						pc_bbmsy = mean(pc10_bbmsy),
						mean_ffmsy = mean(av_ffmsy),
						av_catch = mean(av_catch_Fmsy))

buffer_dat_05

best_buffer_05 <- filter(buffer_dat_05, pc_bbmsy > 0.25) %>%
	group_by(ctrl) %>%
	filter(av_catch == max(av_catch)) 

best_buffer_05

buffer_dat_20 <- filter(dat, rea_yr == "20") %>%
	group_by(buffer, ctrl) %>%
	summarise(mean_bbmsy = mean(av_bbmsy),
						pc_bbmsy = mean(pc10_bbmsy),
						mean_ffmsy = mean(av_ffmsy),
						av_catch = mean(av_catch_Fmsy))

buffer_dat_20

best_buffer_20 <- filter(buffer_dat_20, pc_bbmsy > 0.25) %>%
	group_by(ctrl) %>%
	filter(av_catch == max(av_catch)) 

best_buffer_20

```

After 5 years using true data, 80% buffer is sufficient at keeping 90% of stocks on average (across sp and harvest dynamics) above 25%Bmsy, while maximising catch.

So we should try 100% and 90%.

### Trade-offs between objectives - NOT FIXED FOR BUFFERS

```{r radar_plots}
dat_OW_5yr <- read.csv(file = "../data-generated/summary_stats/dat_OW_5yr_table.csv")

#package - fmsb
library(fmsb)

#set min and max values per each axix
maxmin <- data.frame(
	prop_stocks_not_overfished = c(1, 0),
	av_bbmsy=c(1.25,0),
	prop_stocks_no_overfishing = c(1, 0),
	#av_catch = c(1.25, 0),
	av_catch_Fmsy = c(1.25, 0)) # check # TODO

ctrl_col <- RColorBrewer::brewer.pal(5,"Paired")

# #make dataset
# summary_OW5yr_BC <- dat_OW_5yr %>%
# 	filter(sp == "BC") %>%
# reshape::cast(ctrl ~ variable, margins = FALSE)
# 
# #including only metrics we are interested in for radar plots
# radar_OW5yr_BC <- summary_OW5yr_BC[,c(1,3,4,7,9)] 
# 
# #re order rows so that BAU is at the bottom - for colour order in pallette
# radar_OW5yr_BC <- radar_OW5yr_BC[c(2:5,1),-1]
# 
# radar_OW5yr_BC <- rbind(maxmin,radar_OW5yr_BC)
# 
# dat_radar <- list(radar_OW5yr_BC=radar_OW5yr_BC,radar_OW5yr_SA=radar_OW5yr_SA,radar_OW5yr_CR=radar_OW5yr_CR)

sp_lookup_5 <- filter(sp_lookup, Symbol != "BF") %>%
	droplevels()

#make graph with all species
#pdf(file= "plots/radar_plot.pdf",width = 8, height = 12)
png(filename = "../plots/radar_plot.png",width = 8, height = 12, units = "in",res = 600)
op <- par(mar=c(1, .5, 1, .5),mfrow=c(3, 2))
lapply(sp_lookup_5$Symbol, function(i) { 
	
	summary_OW5yr <- dat_OW_5yr %>%
		filter(sp == i) %>%
		reshape::cast(ctrl ~ variable, margins = FALSE)
	
	#including only metrics we are interested in for radar plots
	# av_bbmsy, av_catch, prop_stocks_not_overfished, prop_stock_no_overfishing
	radar_OW5yr<- summary_OW5yr[,c(1,2,3,8,9)]  #change to be catch_relFmsy
	radar_OW5yr <- radar_OW5yr[c(2:5,1),-1]
	radar_OW5yr <- rbind(maxmin,radar_OW5yr)
	
	radarchart(radar_OW5yr,axistype=3, seg=5, vlabels=c("Prop stocks\nnot heavily overfished","Median\nstatus", "Prop stocks with\nno overfishing", "Median\nyield"),
						 title= sp_lookup$Name[match(i,sp_lookup$Symbol)], axislabcol = "black", vlcex=1, pcol=ctrl_col, caxislabels = c("0","","","","","1"),plty=rep(1,5),plwd = rep(2,5))
})
dev.off()
#par(op)

```

